TrenchR: an R package for transparent environmental and ecological biophysics

### 2020-02-05 Manuscript_full.Rmd
fixed plot axis label

Let us first prepare the environmental data for analysis. We will need to estimate hourly air and soil temperatures and radiation. We start by estimating day of year and the timing of sunrise and sunset:
```{r}
library(TrenchR)
#set up input data as variables
lat=35.69; lon= -105.944; elev=2121
Tmin=10; Tmax=25; Tmin_s=15; Tmax_s=30
V=0.5
#assumptions
tau=0.7; rho=0.6
Tb0=25

@@

We assume, as in generally done for lizards, that heat exchange associated with metabolism and evaporation is negliglible:
```{r}
Qmet= 0.1
Qevap= 0.1
```

@@

```{r}
plot(1:24, (Te-273), type="l", xlab="Hour", ylab="Temperature (°C)", col="blue") #Gates
points(1:24, Te2-273, type="l", col="blue", lty="dotted") #Campbell
points(1:24, Te3, type="l", col="blue", lty="dashed") #Buckley 2008
#points(1:24, Te4, type="l", col="red", lty="solid") #Fei et al.
points(1:24, Ta, type="l", col="orange")
points(1:24, Ts, type="l", col="purple")

>>>>

Let us first prepare the environmental data for analysis. We will need to estimate hourly air and soil temperatures and radiation. We start by estimating day of year and the timing of sunrise and sunset:
```{r}
library(TrenchR)

#set up input data as variables
lat=35.69; lon= -105.944; elev=2121
Tmin=10; Tmax=25; Tmin_s=15; Tmax_s=30
V=0.5
#assumptions
tau=0.7; rho=0.6
Tb0=25

@@

We assume, as in generally done for lizards, that heat exchange associated with metabolism and evaporation is negliglible:
```{r}
Qmet= 0
Qevap= 0
```

@@

```{r}
par(mar=c(5, 4, 4, 8) + 0.1)
plot(1:24, (Te-273.15), type="l", xlab="Hour", ylab="Temperature (°C)", col="blue") #Gates
points(1:24, Te2-273.15, type="l", col="blue", lty="dotted") #Campbell
points(1:24, Te3, type="l", col="blue", lty="dashed") #Buckley 2008
#points(1:24, Te4, type="l", col="red", lty="solid") #Fei et al.
points(1:24, Ta, type="l", col="orange")
points(1:24, Ts, type="l", col="purple")
